---
title: "Traffic Data Analysis"
output: html_document
---


```{r}
library(ggplot2)
library(dplyr)
library(knitr)
library(stargazer)
```

# Data processing

```{r, tidy=TRUE, cache=TRUE}
be2olak.data <- read.csv("all-semi-unique.csv")
summary(be2olak.data) %>% kable()
str(be2olak.data) %>% kable()
```


***

By analyzing the distribution of some columns, I found that some of the columns only have one value, so these columns are not needed and should be deleted from the data.


The columns that will be deleted are the following:

* ad.aid
* ad.bgcl
* ad.bgcls
* ad.fncl
* ad.fncls
* ad.lid
* ad.logo
* ad.logo2x
* ad.logoAndroidS
* ad.logoAndroidH
* ad.cm
* ad.url
* ad.g
* rd.cl
* rd.rp.type

***

```{r, tidy=TRUE, cache=TRUE}
be2olak.data <- subset(be2olak.data, select=-c(2:14,22,34))
```


```{r, tidy=TRUE, cache=TRUE}
summary(be2olak.data) %>% kable()
str(be2olak.data) %>% kable()
```

```{r, tidy=TRUE, cache=TRUE}
be2olak.data[duplicated(be2olak.data[,2:ncol(be2olak.data)]),]
stargazer(be2olak.data, type = "text", title = "Descriptive statistics")
```

Try the plots:

```{r, tidy=TRUE, cache=TRUE}
be2olak.data %>% head() %>% kable(booktabes=TRUE)
```

***

```{r, eval=F, tidy=TRUE, cache=TRUE}
library(rmarkdown)
render("data-analysis.Rmd")
```
